### 2024-11-04 scripts/05-exploratory_data_analysis.qmd
graphing updated
graphing updated
result section updated
bug fixed, Paper graphing updated, readme updated
Paper graphing updated, readme updated, bug fixd
Update 05-exploratory_data_analysis.qmd
add install packages

#### Workspace setup ####

@@

library(rstanarm)

@@

@@

print(unique_methodologys)

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Workspace setup ####

install.packages("tidyverse")
install.packages("patchwork")
install.packages("moments")

@@

@@

Trump_test <- read_parquet(here::here("data/02-analysis_data/02-Testing/test_Trump.parquet"))
Harris_test <- read_parquet(here::here("data/02-analysis_data/02-Testing/test_Harris.parquet"))

@@

print(length(unique_methodologys))
